---
title: 'Dynamic systems with more than one dependent variable'
author: "Kristina Glass and Liane Chen"
output:
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sensitivity)
library(tidyverse)
library(deSolve)
library(lhs)
library(purrr)
library(ggpubr)
```

a) your hunting model
```{r}
setwd(here::here()) 
source("lotvmodK_new.R")
```

b) your exploration (e.g how you tested different hunting levels and how you defined a stability metric

```{r}
# Parameter values
pars = list(rprey=0.95, alpha=0.01, eff=0.6, pmort=0.4, K=2000)

# Initial population values
init_pop = c(prey = 1000, pred = 50)

# Time sequence for simulation
times = seq(0, 100, by=0.1)

# Function to run simulation and plot results
run_simulation = function(hunt_prey, hunt_pred, min_prey) {
  # Update parameters with hunting rates and minimum prey
  pars$hunt_prey = hunt_prey
  pars$hunt_pred = hunt_pred
  pars$min_prey = min_prey
  
  # Run the model
  out = ode(y = init_pop, times = times, func = lotvmodH, parms = pars)
  
  # Plot the results
  matplot(out[, "time"], out[, 2:3], type = "l", xlab = "Time (days)", ylab = "Population",
          col = c("blue", "red"), lty = 1, lwd = 2)
  legend("topright", legend = c("Prey", "Predator"), col = c("blue", "red"), lty = 1, lwd = 2)
}

# Example exploration with different hunting levels and minimum prey populations
par(mfrow = c(2, 2))
run_simulation(hunt_prey = 0.01, hunt_pred = 0.02, min_prey = 500)
title(main = "hunt_prey = 0.01, hunt_pred = 0.02, min_prey = 500")
run_simulation(hunt_prey = 0.02, hunt_pred = 0.02, min_prey = 500)
title(main = "hunt_prey = 0.02, hunt_pred = 0.02, min_prey = 500")
run_simulation(hunt_prey = 0.01, hunt_pred = 0.01, min_prey = 300)
title(main = "hunt_prey = 0.01, hunt_pred = 0.01, min_prey = 300")
run_simulation(hunt_prey = 0.02, hunt_pred = 0.01, min_prey = 300)
title(main = "hunt_prey = 0.02, hunt_pred = 0.01, min_prey = 300")
```


c) provides you estimated sustainable hunting level. and a few sentences justifying this choice 

**We chose these values to ensure that prey populations stay above the minimum threshold to sustain the needs of predations, while also allowing for some sustainable hunting. With min prey levels at both 300 and 500, predator and prey populations generally stay in sync with each other**